---
geometry: margin=1in
output:
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = '../')
```

**Project:**`r CIDAtools::ProjectName()`
**PI:**`r CIDAtools::ProjectPI()`  
**Prepared By:**Caroline Ledbetter    
**Date:** `r paste(format(Sys.Date(), '%m/%d/%Y'))`  

```{r setup, include=FALSE}
load(file = 'DataProcessed/cleaned_model.RData')
load(file = 'DataProcessed/Results.RData')
library(tidyverse)
library(kableExtra)
```

# Major Changes
* Age Unknown and Sex Unknown have been removed
* Percent Male has been removed as a predictor because it is now perfectly 
collinear with female. 
* Missing sex and age has been imputed
* Uncommon serotypes have been grouped with regression
* Season has been replaced with month
* Additional data cleaning to pull missing serotypes from text fields
* If more than one serotype was present priority is first given to confirmed 
over suspected then to the serotype with the most number of cases - multiple 
serotypes is no longer an option. 



```{r missing}
analysis %>% filter_all(any_vars(is.na(.))) %>% 
  count(year, name = 'missing_n') -> tmp
analysis %>% count(year) %>% full_join(tmp) %>% 
  mutate(pct = missing_n/n*100) %>% 
  select(Year = year, N = n, `Pct Missing Any` = pct) -> tmp

analysis %>% 
  group_by(year) %>% 
  summarise_all(~ sum(is.na(.))/n()*100) %>% 
  select(Year = year, Sex = percent_male, Age = percent_age_under1, 
         Hospitalized = hosp_percent, Geography = geography, 
         Serotype = serotype) %>% 
  full_join(x = tmp, y = .) %>% 
  kable(caption = "Missing Data", digits = 0) %>% 
  add_header_above(c(' ' = 3, 'Percent Missing each Variable' = 5)) %>% 
  kable_styling() 
```


**Other, Meat-Poultry Other and Produce Other Excluded**  


```{r, fig.width= 9}
no_other$plots
```

```{r }
no_other$brier_scores %>% 
  kable() %>% 
  kable_styling()

```

**Other and Dairy Excluded**  


```{r, fig.width= 9}
collapsed$plots
```

```{r }
collapsed$brier_scores %>% 
  kable() %>% 
  kable_styling()

```